---
title: "Web Scraping"
subtitle: "UNSDGLEARN: Breaking the Si"
author: "Caitlin Sarro"
date: "2/9/2022"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```
***
CONTEXT TEXT

In general, remember, the basic **workflow for scraping static webpages** is the following.

**Step 1.** Load the packages

```{r, message=F}
#install.packages("")
library(RSelenium)
library(tidyverse)
library(rvest)
library(stringr)
library(readr)

library(reshape2)
library(dplyr)

library(purrr)
library(tibble)
```



```{r}
#SDG Academy https://sdgacademy.org/courses/
```

# Scraping multiple pages `r emo::ji("robot")`

Whenever you want to really understand what's going on within the functions of a new R package, it is very likely that there is a relevant article published in the [Journal of Statistical Software](https://www.jstatsoft.org/index). Let's say you are interested in how the journal was doing over the past years.

**Step 1.** Inspect the source. Basically, follow steps to extract the Xpath information.
```{r, eval=F}
#browseURL("https://sdgacademy.org/courses/")
```

**Step 2.** Parse the page source.

```{r}
#SDG Academy
#start RSelenium

system('docker kill $(docker ps -q)')
Sys.sleep(2)
system('docker run -d -p 4445:4444 selenium/standalone-chrome')
Sys.sleep(2)
system('docker container ls')

#rstudioapi::terminalExecute('java -Dwebdriver.chrome.driver="C:/Users/caitl/Documents/R #Files/selenium/chromedriver.exe" -jar "C:/Users/caitl/Documents/R #Files/selenium/selenium-server-standalone-3.141.59.jar" -port 4567')
#standalone-chrome-debug:latest


remDr <- remoteDriver(
        remoteServerAdd = "localhost",
        port = 4445L,
        browser = "chrome", chromever = "94.0.4606.61" 
)

remDr$open()

#navigate to your page
remDr$navigate("https://sdgacademy.org/courses/")

#scroll down 5 times, waiting for the page to load at each time
for(i in 1:5){      
remDr$executeScript(paste("scroll(0,",i*10000,");"))
Sys.sleep(3)    
}

#get the page html
page_source <-remDr$getPageSource()

#pageEls  <- remDr$findElements(using = "css", "#contents #details #meta")

sdgacademy <- read_html(page_source[[1]])


```


**Step 3.** Extract information.
```{r}
#Parse out TITLES for the training courses
parsed_nodes <- html_nodes(sdgacademy, 
                           xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "desktop", " " ))]//a')
titles_acad <- html_text(parsed_nodes)
titles_acad

#Parse out WEBLINKS to the courses
weblink_acad <- sdgacademy  %>% html_nodes("div.course-item") %>% html_attr("data-link")
weblink_acad

```

```{r}
# Subpage scraping
# Define the AUDIENCE worker function
scraper <- function(weblink_acad) {
  read_html(weblink_acad) %>% 
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "course-detail", " " ))] | //strong') %>% 
    html_text() %>% 
    enframe("id", "audience")
}

# Iterate over the urls, applying the function each time
audience_acad <- map_dfr(weblink_acad, scraper, .id = "id")


#Combine into single columns

audience_acad <- audience_acad %>%
 group_by(id) %>%
 summarize(audience = str_c(audience, collapse = ", "))

#sort

audience_acad$id <- as.numeric(audience_acad$id)

audience_acad <- audience_acad[order(audience_acad$id, decreasing = FALSE),] 

audience <- as.vector(audience_acad$audience)

```



```{r}
weblink_acad
# Define the AUTHOR worker function
scraper <- function(weblink_acad) {
  read_html(weblink_acad) %>% 
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "fauclty-degree", " " ))]') %>% 
    html_text() %>% 
    enframe("id", "author")
}

# Iterate over the urls, applying the function each time
authors_acad <- map_dfr(weblink_acad, scraper, .id = "id")
authors_acad


#Combine into single columns

authors_acad <- authors_acad %>%
 group_by(id) %>%
 summarize(author = str_c(author, collapse = ", "))


authors_acad$id <- as.numeric(authors_acad$id)

authors_acad[order(authors_acad$id, decreasing = FALSE),] 


authors <- as.vector(authors_acad$author)


```

```{r}
#adding in authors for #16

id <- c(16)
author <- c("Natural Resource Governance Institute (NRGI), the Columbia Center on Sustainable Investment (CCSI), the CONNEX Support Unit, GIZ, the European Union")

authors_gooddeal <- data.frame(id, author)

authors_gooddeal$id <- as.numeric(authors_gooddeal$id)

#Add new row
authors_acad[nrow(authors_acad) + 1,] <- authors_gooddeal


#reorganize

authors_acad <- authors_acad[order(authors_acad$id, decreasing = FALSE),] 

author <- as.vector(authors_acad$author)
```

```{r}

# Parse out the SDGs
test <-"https://sdgacademy.org/course/governance-for-transboundary-freshwater-security/"
weblink_test <- read_html(test)

test_alt <- weblink_test %>% 
  html_nodes("#goal-image .img src") %>%
  html_attr("alt")
test_alt


test_alt <- html_nodes(weblink_test, 
                           xpath = '//p[(((count(preceding-sibling::*) + 1) = 5) and parent::*)]') %>% 
    html_text()
test_alt


```


```{r}
# DELETE THIS
# Define the AUTHOR worker function
scraper <- function(weblink_acad) {
  read_html(weblink_acad) %>% 
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "text", " " ))]//p[(((count(preceding-sibling::*) + 1) = 3) and parent::*)]') %>% 
    html_text() %>% 
    enframe("id", "author")
}

############################################
list("Agenda 2030" = "Private: Just wheel",
                "2" = "lemmon",
                "3" = "orange",
                "4" =c("apple", "lemon", "grape"),
                "5"=c("cheery", "lemon", "grape"),
                "6"=c("apple", "lemon", "apple"))

```

```{r}
# Define the SDGs  worker function
scraper <- function(weblink_acad) {
  read_html(weblink_acad) %>% 
html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "goals", " " ))] | //*[contains(concat( " ", @class, " " ), concat( " ", "goal-image", " " ))]//img') %>%
  html_attr("alt") %>%
    enframe("id", "SDGs")
}

# Iterate over the urls, applying the function each time
SDGs_acad <- map_dfr(weblink_acad, scraper, .id = "id")

# Cleanup, remove NA
SDGs_acad <- na.omit(SDGs_acad) 

# Cleanup, remove Duplicates
SDGs_acad <- SDGs_acad[!duplicated(SDGs_acad),]


SDGs_acad$SDGs[SDGs_acad$SDGs == "Private: Just wheel"] <- "Agenda 2030"
SDGs_acad$SDGs[SDGs_acad$SDGs == "No Poverty"] <- "SDG1"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Zero Hunger"] <- "SDG2"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Good Health and Well-Being"] <- "SDG3"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Quality Education"] <- "SDG4"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Gender Equality"] <- "SDG5"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Clean Water and Sanitation"] <- "SDG6"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Affordable and Clean Energy"] <- "SDG7"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Decent Work and Economic Growth"] <- "SDG8"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Industry, Innovation and Infrastructure"] <- "SDG9"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Reduced Inequalities"] <- "SDG10"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Sustainable Cities and Communities"] <- "SDG11"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Responsible Consumption and Production"] <- "SDG12"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Climate Action"] <- "SDG13"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Life Below Water"] <- "SDG14"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Life on Land"] <- "SDG15"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Peace, Justice and Strong Institutions"] <- "SDG16"
SDGs_acad$SDGs[SDGs_acad$SDGs == "Partnerships for the Goals"] <- "SDG17"
SDGs_acad
```



```{r}
#Combine into single columns

sdgs_combined <- SDGs_acad %>%
 group_by(id) %>%
 summarize(SDGs = str_c(SDGs, collapse = ", "))


sdgs_combined$id <- as.numeric(sdgs_combined$id)

sdgs_combined <- sdgs_combined[order(sdgs_combined$id, decreasing = FALSE),] 


SDGs <- as.vector(sdgs_combined$SDGs)

```


```{r}
#merge into single dataframe

sdgacad_df <- data.frame(titles_acad, authors_acad, weblink_acad, sdgs_combined, audience_acad )

#remove redundant cols
sdgacad_df <- mutate(sdgacad_df, id=NULL, id.1=NULL, id.2=NULL)


```

```{r}
#export as CSV
write.csv(sdgacad_df,"C:/Users/caitl/Documents/GitHub/thesis/exports/sdgacademy.csv", row.names = TRUE)

```

```{r}
#missing keywords and tags

```


```{r}
#not working?
#system("sudo docker pull selenium/standalone-chrome",wait=T)
#Sys.sleep(5)
#system("sudo docker run -d -p 4445:4444 selenium/standalone-chrome",wait=T)
#Sys.sleep(5)
#remDr <- remoteDriver(port=4445L, browserName="chrome")
#Sys.sleep(15)
#remDr$open()

